### 2018-11-25 chapters/3-results.tex
more readable results

For each of the five image types, a ROC analysis for each texture feature was
performed. The resulting best features are shown in
Table~\ref{tab:texture_imagetype}. The feature that best discriminated low from
high Gleason score was MBB-GLCM homogeneity in T₂w with AUC of 0.84. A
similar analysis was performed for the first-order statistical features; results
for the best statistical features are shown in Table~\ref{tab:stats_imagetype}.
Although the best statistical features had good performance for most of the
modalities, they did not out-perform the best texture features. Some of the
high-ranking features are visualized in Figure~\ref{fig:tmap}. In addition, ROC
curves for best statistical and texture features are presented in
Figure~\ref{fig:roc}.

>>>>

ROC analysis was performed for each texture feature. The resulting best features
are shown in Table~\ref{tab:texture_imagetype}. The best one was MBB-GLCM
homogeneity in T₂w with AUC of 0.84.

A similar analysis was performed for the first-order statistical features;
results are shown in Table~\ref{tab:stats_imagetype}. Although the best
statistical features had good performance for most of the modalities, they did
not out-perform the best texture features.

Some of the high-ranking features are visualized in Figure~\ref{fig:tmap}. In
addition, ROC curves for best statistical and texture features are presented in
Figure~\ref{fig:roc}.
